The eclipse of ASASSN-21qj

### 2022-11-20 src/tex/ms.tex
[showyourwork] overleaf sync

   \author{M. Kenworthy
          \inst{1}
          \and
          Arttu Sainio
          \inst{2}
          \and
          Eric E. Mamajek
          \inst{3}
          \and
          Joeseph Masiero
          \inst{4}
          \and 
          Amy Mainzer
          \inst{4}
          \and
          Joeseph (Davy) Kirkpatrick
          \inst{4}
          \and 
          Richelle F. van Capelleveen
          \inst{1}
          \and
          Grant M. Kennedy
          \and
          Ludmila Carone
          \and
          NEOWISE authorship list
          \inst{4}
          \and
          AAVSO observers
          \and
          St\'{e}phane Charbonnel
          \and
        Olivier Garde
        \and
        Pascal Le D\^{u}
        \and
        Lionel Mulato
        \and
        Thomas Petit
          }

   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
         \and
             Arttu's address\\
    \and
    JPL
    \and
    Caltech/IPAC, 1200 E California Blvd, Mail Code 100-22, Pasadena, CA 91125, USA
    \and
    NEOWISE
    \and
    AAVSO people
    \and
    Space Research Institute, Austrian Academy of Sciences, Schmiedlstrasse 6, A-8042 Graz, Austria
}
   \date{Received XXXX; accepted XXXX}

@@

\begin{figure*}
   \begin{centering}
   \includegraphics[width=\textwidth]{figures/2spot_spectrum.pdf}
      \caption{Spectrum of \asas\ showing features of a typical G type star.
              }
              \label{fig:2spotspectrum}
              \script{plot_2spot_spectrum.py}
              \end{centering}
       \end{figure*}

@@

\begin{figure*}
   \begin{centering}
   \includegraphics[width=\textwidth]{figures/velocity_constraints.pdf}
      \caption{Circular velocity as a function of semimajor axis, and the effective temperature of dust as a function of semi-major axis.
              }
              \label{fig:veloc_cons}
              \script{calc_velocity_bounds_plots.py}
              \end{centering}
       \end{figure*}

>>>>

   \author{Matthew A. Kenworthy
          \inst{1}
          \and
          Arttu Sainio
          \inst{1}
          \and
          Eric E. Mamajek
          \inst{1}
          \and
          Joeseph Masiero
          \inst{1}
          \and
          Amy Mainzer
          \inst{1}
          \and
          Joeseph (Davy) Kirkpatrick
          \inst{1}
          \and 
          Richelle F. van Capelleveen
          \inst{1}
          \and
          Grant M. Kennedy
                    \inst{1}
          \and
          Ludmila Carone
                    \inst{1}
          \and
          NEOWISE authorship list
                    \inst{1}
          \and
          AAVSO observers
                    \inst{1}
          \and
          St\'{e}phane Charbonnel
                    \inst{1}
          \and
        Olivier Garde
                  \inst{1}
        \and
        Pascal Le D\^{u}
                  \inst{1}
        \and
        Lionel Mulato
                  \inst{1}
        \and
        Thomas Petit
                  \inst{1}
          }

   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
%         \and
%             Arttu's address\\
%    \and
%    JPL
%    \and
%    Caltech/IPAC, 1200 E California Blvd, Mail Code 100-22, Pasadena, CA 91125, USA
%    \and
%    NEOWISE
%    \and
%    AAVSO people
%    \and
%    Space Research Institute, Austrian Academy of Sciences, Schmiedlstrasse 6, A-8042 Graz, Austria
}
   \date{Received XXXX; accepted XXXX}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=0.5\textwidth]{figures/2spot_spectrum.pdf}
\caption{Spectrum of \asas\ showing features of a typical G type star.}
        \label{fig:2spotspectrum}
        \script{plot_2spot_spectrum.py}
    \end{centering}
\end{figure}

@@

\begin{figure}
    \begin{centering}
    \includegraphics[width=0.5\textwidth]{figures/velocity_constraints.pdf}
    \caption{Circular velocity as a function of semimajor axis, and the effective temperature of dust as a function of semi-major axis.
              }
    \label{fig:veloc_cons}
    \script{calc_velocity_bounds_plots.py}
    \end{centering}
\end{figure}
